\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}

\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\vspace{2pt}\titlerule\vspace{4pt}]
\titlespacing{\section}{0pt}{8pt}{4pt}

\setlist[itemize]{leftmargin=1.3em,itemsep=1pt,topsep=2pt,parsep=0pt}

\newcommand{\role}[4]{%
  \textbf{#1}\hfill\textbf{#3}\\
  \textit{#2}\hfill\textit{#4}\vspace{2pt}%
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt,label={},itemsep=4pt,topsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSubheading}[4]{%
  \item \textbf{#1}\hfill\textbf{#2}\\
  \textit{#3}\hfill\textit{#4}\vspace{2pt}%
}

\begin{document}

\begin{center}
  {\LARGE \scshape \textbf{Vishal Munday}}\\[3pt]
  {\normalsize Backend Tech Lead $|$ AI \& Cloud-Native Systems}\\[4pt]
  \small
  Jind, Haryana, India $\bullet$ Phone: +91 8570090556 $\bullet$
  Email: \href{mailto:im@vishu.dev}{im@vishu.dev}\\
  Portfolio: \href{https://vishu.dev}{vishu.dev} $\bullet$
  LinkedIn: \href{https://linkedin.com/in/vishu7im/}{linkedin.com/in/vishu7im} $\bullet$
  GitHub: \href{https://github.com/vishu7im}{github.com/vishu7im}
\end{center}

\section{Professional Summary}
Backend Tech Lead with 3+ years of experience designing and scaling production-grade backend systems, GenAI applications, and cloud-native platforms. Proven expertise in microservices, real-time systems, and third-party integrations across supply chain, insurance, hospitality, and SaaS domains. Adept at leading backend teams and translating complex requirements into reliable, high-performance solutions.

\section{Technical Skills}
\textbf{Languages:} JavaScript, TypeScript, Python, SQL, HTML, CSS\\
\textbf{Frameworks:} Node.js, Express.js, React.js, Next.js, Tailwind CSS\\
\textbf{Databases:} MySQL, MongoDB, PostgreSQL, Redis\\
\textbf{Cloud \& DevOps:} AWS, Firebase, Docker, GitHub Actions\\
\textbf{AI / GenAI:} LangChain.js, LangGraph, RAG, Agent-to-Agent (ADK), AI Agents, Mem0, GuardRails, LiveKit, WebRTC

\section{Professional Experience}
\role{EdgeNRoots Solutions Pvt Ltd}{Backend Tech Lead}{May 2024 -- Present}{Remote (Full-Time)}
\begin{itemize}
  \item Led backend and AI initiatives across supply chain, insurance, hospitality, and SaaS clients, delivering scalable production-grade systems and mentoring the backend team.
  \item Architected MetaOS, a WhatsApp CRM platform with campaigns, automation, analytics, and AI-powered engagement, cutting manual customer-response effort by an estimated 60\%.
  \item Built Aaxel Voice Agent, a real-time voice-to-voice AI agent on LiveKit and WebRTC, achieving low-latency conversational experiences and production-scale reliability.
\end{itemize}

\role{Icomply Lifescience Solution Pvt Ltd}{Full Stack Developer (Intern + Part-Time)}{Oct 2022 -- Jun 2024}{Remote}
\begin{itemize}
  \item Integrated AS2 gateway and XML templates to enable secure, compliant B2B data exchange for life-science clients.
  \item Designed backend APIs powering dynamic user interfaces, improving frontend responsiveness and data throughput.
  \item Optimized application performance, increasing system reliability and reducing average response times by an estimated 30\%.
\end{itemize}

\section{Key Projects}
\textbf{FabricatorOS -- uPVC SaaS Platform} \hfill \textit{Node.js, Express, PostgreSQL, Prisma, Docker, React}
\begin{itemize}
  \item Developed a multi-tenant SaaS platform for uPVC and aluminium fabricators covering quotation, work order, and production management.
  \item Engineered a dynamic window/door configuration engine with live SVG rendering, cutting lists, material optimization, and multi-span topology generation.
\end{itemize}

\textbf{TalkTive -- WhatsApp CRM Platform} \hfill \textit{Node.js, Express.js, Redis, WhatsApp API, Microservices}
\begin{itemize}
  \item Led backend development of inbox, campaigns, approvals, analytics, and third-party integration modules for high-volume messaging.
  \item Designed scalable microservice APIs, asynchronous pipelines, and AI-powered automation agents for customer support orchestration.
\end{itemize}

\section{Education}
  \resumeSubHeadingListStart
   \resumeSubheading
      {BITS Pilani (WILP)}{2026 -- Ongoing}
      {B.Tech. Artificial Intelligence and Machine Learning}{Pilani, India}
   \resumeSubheading
      {Guru BrahmaNand Ji Govt. Polytechnic}{2021 -- 2024}
      {Diploma in Computer Engineering}{Karnal, Haryana}
  \resumeSubHeadingListEnd

\end{document}
